An efficient feedback calibration algorithm for direct imaging radio telescopes

### 2016-03-02 cal_demo/ms.tex
added reference to PyGSM

Figure~\ref{fig:data_images} shows the improvement in the images due to our calibration. The left panel shows the uncalibrated image integrated over 51.2 ms, 29 kHz. Cyg~A is prominent near the center of the image, and Cas~A is also clearly visible in the upper right. The middle panel shows the image produced after calibration with identical integration time and bandwidth. The sidelobes ({\bf or is it better to call them speckles due to uncalibrated phases because sidelobes are typically associated with the psf and not with calibration?}) throughout the image are significantly suppressed, and the galactic plane is much more evident, despite only modeling Cyg~A and Cas~A. We also note that the feature just to the right of Cyg~A is dimmer in the calibrated image, better matching the expected flux from the global sky model (GSM, \citealt{deo08}). We show the GSM modulated by two factors of the LWA power pattern in the right panel of figure~\ref{fig:data_images} for reference.

>>>>

Figure~\ref{fig:data_images} shows the improvement in the images due to our calibration. The left panel shows the uncalibrated image integrated over 51.2 ms, 29 kHz. Cyg~A is prominent near the center of the image, and Cas~A is also clearly visible in the upper right. The middle panel shows the image produced after calibration with identical integration time and bandwidth. The sidelobes ({\bf or is it better to call them speckles due to uncalibrated phases because sidelobes are typically associated with the psf and not with calibration?}) throughout the image are significantly suppressed, and the galactic plane is much more evident, despite only modeling Cyg~A and Cas~A. We also note that the feature just to the right of Cyg~A is dimmer in the calibrated image, better matching the expected flux from the global sky model (GSM, \citealt{deo08}). We show the GSM\footnote{using the PyGSM module by D.~C.~Price to import the GSM, \textcolor{red}{insert reference}} modulated by two factors of the LWA power pattern in the right panel of figure~\ref{fig:data_images} for reference.
